---
title: "QCBS Open Science Workshop"
author: "Monica Granados"
date: '2017-04-19'
output: pdf_document
---

# Mr. Verneaux and his magical adventures looking for fish in the Doubs River. 

## Methods
Fish were collected from the Doubs River which runs near the France–Switzerland border in the Jura Mountains. The fish are used to biological indicators for the different characterized eco-regions. 

## Results

```{r include=FALSE}
#install packages
require(RCurl)
require(tidyr)
require(ggplot2)
doubs.URL <- getURL("https://raw.githubusercontent.com/Monsauce/QCBS-Open-Science-Workshop/master/doubsspe.csv")
doubs<-read.csv(text=doubs.URL) 

#the data is in wide form so let's convert it to long
doubs.long<-gather(doubs, species, count, CHA:ANG)
```

The data set had a total richness of `r length(unique(doubs.long$species))`

```{r, message=FALSE, fig.width=5, fig.height=6.5, echo=FALSE}
#note you can set the size parameters of the figure 
Figure.1<-ggplot(doubs.long, aes(count))+geom_histogram()+facet_wrap(~X)+theme_minimal()+xlab("Number of individuals")+ylab("Number of species")

plot(Figure.1)  
```

Figure 1. Histogram for each site (1-30) of the frequency of number of individuals caught across species. 